Out-of-Sample Comparisons of Overfit Models

### 2014-02-18 paper.tex
Edit introduction to setup/assumptions section

\section{Setup and Assumptions}\label{sec:assumptions}
We will set up our models and notation first, then list the assumptions
required for our results.

\subsection{Notation and Forecasting Environment}
We assume the following forecasting environment. There are two
competing linear models that give forecasts for the target,
$y_{t+\h}$:
\[
y_{t+\h} = x_{1t}'\theta_1 + \e_{1,t+h}, \quad\text{and}\quad
y_{t+\h} = x_{2t}'\theta_2 + \e_{2,t+h};
\]
$t = 1,\dots,T-h$, $\h$ is the forecast horizon, and the
variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
The coefficients $\theta_1$ and $\theta_2$ minimize the population
Mean Square Error, so
\begin{equation*}
  \theta_i = \argmin_\theta \sum_{t=1}^{T-\h} \E (y_{t+\h} - x_{it}'\theta)^2,
\end{equation*}
making $\e_{i,t+\h}$ uncorrelated with $x_{i,t}$. Let
\begin{equation*}
  \mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)
\end{equation*}
with $x_t$ the vector of all elements of $x_{1t}$ and $x_{2t}$ after
removing duplicates, and let $\E_t$ and $\var_t$ denote the
conditional mean and variance given $\mathcal{F}_t$.  The first model
uses $K_1$ regressors, and the second uses $K_2$.  Without loss of
generality, assume that $K_1 \leq K_2$.  We will allow $K_1$ and $K_2$
to vary with $T$, so a stochastic array underlies all of our
asymptotic theory, but we suppress that notation to simplify the
presentation.

>>>>

\section{Setup and Assumptions}\label{sec:assumptions}
The first part of this section will describe the environment in detail
and set up our models and notation. The second part will list the
assumptions underlying our theoretical results.

\subsection{Notation and Forecasting Environment}
We assume the following forecasting environment. There are two
competing linear models that give forecasts for the target,
$y_{t+\h}$:
\[
y_{t+\h} = x_{1t}'\theta_1 + \e_{1,t+h}, \quad\text{and}\quad
y_{t+\h} = x_{2t}'\theta_2 + \e_{2,t+h};
\]
$t = 1,\dots,T-h$, $\h$ is the forecast horizon and the
variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
The coefficients $\theta_1$ and $\theta_2$ minimize the population
Mean Square Error, so
\begin{equation*}
  \theta_i = \argmin_\theta \sum_{t=1}^{T-\h} \E (y_{t+\h} - x_{it}'\theta)^2,
\end{equation*}
making $\e_{i,t+\h}$ uncorrelated with $x_{i,t}$; $\e_{i,t+\h}$ may exhibit
serial correlation so both of the linear models may be misspecified.
Let $\mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)$ be the information
set available to the forecaster in period $t$,
with $x_t$ the vector of all stochastic elements of $x_{1t}$ and $x_{2t}$ after
removing duplicates, and let $\E_t$ and $\var_t$ denote the
conditional mean and variance given $\mathcal{F}_t$.  The first model
uses $K_1$ regressors, and the second uses $K_2$.  Without loss of
generality, assume that $K_1 \leq K_2$.  We will allow $K_1$ and $K_2$
to vary with $T$, so a stochastic array underlies all of our
asymptotic theory, but we suppress that notation to simplify the
presentation.
